---
title: "Topic ratings"
author: "Jürgen Schneider"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
    toc: yes
    toc_depth: 2
---

```{r setup, echo = F}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = TRUE)
```

```{r libraries}
library(here)
library(tidyverse) # ohne steh ich nicht auf
library(psych)
library(kableExtra)
```

# Import

Data files are in folder "effsize/data".

```{r import}
topics <- rio::import(here("data/rating_topics.csv"))
```

# ICC

* all raters rated all cases
* raters were not chosen at random

Therefore the line `Single_fixed_raters ICC3` is relevant for us:

```{r ICC}
topic_icc <- ICC(topics%>%dplyr::select(Kirstin:Kristina))
topic_icc
```

Agreement is good with an $ICC = `r round(topic_icc$results$ICC[3], 3)`$ and a $CI_{95}=[`r round(topic_icc$results$'lower bound'[3], 3)`, `r round(topic_icc$results$'upper bound'[3], 3)`]$


# Best ranked topics

Topics ranked by mean score over all 4 raters.

```{r}
topics <- topics %>%
  rowwise() %>%
  dplyr::mutate(rating_mean = mean(c(Kirstin, 
                                     Samuel, 
                                     Juergen, 
                                     Kristina)),
                rating_median = median(c(Kirstin, 
                                         Samuel, 
                                         Juergen, 
                                         Kristina))) %>%
  arrange(desc(rating_mean))

kbl(topics%>%dplyr::select(-c(Kirstin:Kristina))) %>%
  kable_styling(bootstrap_options = "striped", 
                full_width = F, 
                position = "left")
```



# R version

```{r version}
R.Version()
```

# Session info

```{r session}
sessionInfo()
```