---
title: "Reproducible Documentation of Analysis Study 1"
format: 
  html:
    theme: solar
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 4
    embed-resources: true
editor: source
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

# Import of the Data

The data was assessed with the `formr` survey framework [@arslan2020]. The raw data was imported via the following code.

```{r}
#| label: libraries and data import
library(tidyverse)
library(ggforce)
library(lme4)
library(BFpack)
library(hrbrthemes)
library(patchwork)
library(brms)
library(viridis)
load("data/teachers_study1_N40.RData")

set.seed(25051982)
```

# Data Wrangling
```{r}
#| label: data wrangling

# wrangle information on the plot type, ES, ...
plot_info <- study1 %>%
    pivot_longer(2:195, names_to = "variables", values_to = "values", 
                 values_transform = as.character) %>%
    dplyr::filter(str_detect(variables, "plot")) %>% 
    # we only need the rows with info on plots
    tidyr::separate(col = values, into = c("type", "axis", "effsize"), 
                    # separate the info into three columns
                    sep = "_", remove = F) %>%
    dplyr::mutate(plot = variables,       # rename variables for later join
                  type = paste(type, axis, sep = "_")) %>%
    dplyr::select(-variables, -axis)

# wrangle answers to items on each page
item_values <- study1 %>%
    dplyr::select(-c(topic:itemo)) %>%
    pivot_longer(2:169, names_to = "variables", values_to = "values", 
                 values_transform = as.character) %>%
    dplyr::mutate(variables = case_when(      # recode variable names that have
        variables == "sensi_6" ~ "sensi_06",  # accidentally been labeled
        variables == "acccl_6" ~ "acccl_06",  # without zero
        variables == "accu3_6" ~ "accu3_06",
        variables == "accov_6" ~ "accov_06",
        variables == "diffi_6" ~ "diffi_06",
        variables == "infor_6" ~ "infor_06",
        variables == "value_6" ~ "value_06",
        TRUE ~ variables 
    )) %>%
    dplyr::mutate(plot = paste0("plotx_", str_sub(variables, -2, -1)), 
                  # create variable for later join
                  variables = str_sub(variables, 1, -4)) %>%    
    # rename variable names to get a data set 
    # with one line per participant per page
    pivot_wider(id_cols = c(session, plot), names_from = "variables", 
                values_from = "values")


# join the two data sets
study1_w <- full_join(plot_info, item_values, 
                               by = c("session", "plot")) %>% 
    # by participant and page (plot)
    dplyr::select(-values) %>%
    dplyr::mutate(rating_cl = as.numeric(acccl), # some var need to be defined as
                  rating_u3 = as.numeric(accu3), # numeric again
                  rating_ov = as.numeric(accov),
                  diffi = as.numeric(diffi),
                  infor = as.numeric(infor),
                  value = as.numeric(value),
                  effsize = as.numeric(effsize),
                  effsize_cl = case_when( 
                  # there is no negative Cliff's Delta, so we have to compute 
                  # two transformations
                      effsize > 0 ~   (((2*pnorm(effsize/2))-1)/pnorm(effsize/2)),
                  # transform the actual effect size Cohen's d to Cliff's Delta
                      effsize < 0 ~ (- (((2*pnorm(abs(effsize)/2))-1)/pnorm(abs(effsize)/2))) 
                  # transform the actual effect size Cohen's d to Cliff's Delta 
                  # and make it negative as in the item
                  ),
                  effsize_u3 = 1-pnorm(effsize), # reverse so that it fits the direction of the U3 item
                  # transform the actual effect size Cohen's d to Cohen's U3
                  effsize_ov = 2 * pnorm(-abs(effsize) / 2), 
                  # transform the actual effect size Cohen's d to overlap
                  # actual difference of rating relative to depicted effectsize 
                  diff_cl = (rating_cl - effsize_cl)/2,
                  # actual difference of rating relative to depicted effectsize
                  diff_u3 = (rating_u3/100) - effsize_u3,
                  # actual difference of rating relative to depicted effectsize 
                  diff_ov = (rating_ov/100) - effsize_ov,
                  diffi_normed = ((diffi - 1)  / 3) - 1, # transform item to -1 to 1
                  infor_normed = ((infor - 1)  / 3) - 1, # transform item to -1 to 1
                  value_normed = ((value - 1)  / 3) - 1) %>%  # transform item to -1 to 1
    group_by(session) %>% 
    mutate(rating_ov_missconcept = median(rating_ov, na.rm = T) < 68.9,
           rating_u3_missconcept = median(rating_u3, na.rm = T) < 21.2) %>% 
    ungroup() %>% 
    mutate(rating_u3_filtered = ifelse(rating_u3_missconcept == T, NA, rating_u3),
           rating_ov_filtered = ifelse(rating_ov_missconcept == T, NA, rating_ov),
           diff_u3_filtered = (rating_u3_filtered/100) - effsize_u3,
           diff_ov_filtered = (rating_ov_filtered/100) - effsize_ov,
           sensi_binary = ifelse(is.na(sensi), # 1 if NOT "equal"
                                        NA,
                                        as.numeric(!grepl("equal", sensi))),
           sensi_ordinal = ordered(factor(substr(sensi, 55, 100)),
                                   levels = c("inferior",
                                              "equal",
                                              "superior")),
           sensi_binary_filtered = case_when(sensi_ordinal == "equal" ~ 0, 
                                              (sensi_ordinal == "inferior" & 
                                                  effsize < 0) | 
                                                  (sensi_ordinal == "superior" & 
                                                  effsize > 0) ~ as.numeric(NA),
                                              TRUE ~ 1),
           effsize_abs = abs(effsize))

# create a list of u3_misconceptualizers
u3_misconceptualizers <-
    study1_w %>% 
    filter(rating_u3_missconcept == T) %>% 
    pull(session) %>% 
    unique()

# create a list of ov_misconceptualizers
ov_misconceptualizers <-
    study1_w %>% 
    filter(rating_ov_missconcept == T) %>% 
    pull(session) %>% 
    unique()    

### wrangle time stamp data ####################################################
study1_w_timestamp <- 
    read_csv("data/teachers_study1_N40_detailed.csv") %>% 
    # filter participants from study1_w only
    filter(session %in% study1_w$session) %>% 
    # we only need vars sensitivity or accuracy
    dplyr::filter(str_detect(item_name, "sensi|acccl|accu3|accov")) %>%  
    # create var with plot number
    mutate(plot = paste0("plotx_", str_sub(item_name, -2, -1)),
           # recode wrong item labelling
           plot = ifelse(plot == "plotx__6", "plotx_06", plot)) %>% 
    relocate(session, plot) %>% 
    # delete the page number in item name
    mutate(item_name = str_sub(item_name, 1, 5)) %>%  
    pivot_wider(id_cols = c(session, plot), names_from = item_name, 
                values_from = answered_relative) %>% 
    rowwise() %>%
    # what was the time of the first item to be clicked?
    mutate(effic = min(sensi, acccl, accu3, accov, na.rm=T)) %>%
    ungroup() %>% 
    dplyr::select(session, plot, effic, sensi, acccl, accu3, accov) %>% 
    left_join(., study1_w %>% 
                  select(session, plot, type), by=c("session", "plot")) %>% 
    # generate data set so that the six plots from the same type are ordered
    # one after the other (and not 1-24)
    group_by(session, type) %>% 
    arrange(plot) %>% 
    mutate(plotNrWithin = 1:n()) %>%
    ungroup() %>% 
    group_by(plotNrWithin, type) %>% 
    mutate(effic_10righttrunc = ifelse(effic > quantile(effic, .9), NA, effic),
           effic_05righttrunc = ifelse(effic > quantile(effic, .95), NA, effic),
           log_effic_05righttrunc =log(effic_05righttrunc),
           log_effic_10righttrunc = log(effic_10righttrunc),
           plotNrWithin0 = plotNrWithin -1,
           plotNrWithin_factor = as.factor(plotNrWithin)) %>% 
    ungroup()
```

## Accuracy

### Distribution of the Dependent Variables

```{r}
#| label: distribution acc dvs

study1_w %>% 
    select(rating_cl, rating_u3, rating_ov) %>% 
    pivot_longer(
        c(rating_cl, rating_u3, rating_ov),
        names_to = "dependent_variable", 
        values_to = "rated_effectsize"
        ) %>% 
    ggplot(., aes(rated_effectsize)) +
    geom_histogram() +
    facet_wrap(~dependent_variable, scales = "free_x") +
    theme_modern_rc() +
    theme(strip.text = element_text(color = "white"))
```

Somewhat disturbing is the first mode in `accov`. Maybe some users confused `overlap` and `non-overlap`? Another artifact seems to be the first mode in `accu3`.

### Are there Constant Misconceptions per Persons?

```{r}
#| label: misconceptiosn per person
ggplot(study1_w %>% 
    select(rating_cl, rating_u3, rating_ov, effsize, effsize_cl, session) %>% 
    pivot_longer(
        c(rating_cl, rating_u3, rating_ov),
        names_to = "operationalization", 
        values_to = "judged_effectsize"
        ),
    aes(judged_effectsize, as.numeric(as.factor(session)),
        color = session)
        ) +
    geom_jitter(height = 0) +
    facet_wrap(~ operationalization, scales = "free_x") +
    theme_modern_rc() +
    theme(legend.position = "none",
          strip.text = element_text(color = "white"))
```

It seems to be so, as ....

### Association of Ratings and Actual Effect Size

```{r}
#| label: acc associations
study1_w %>% 
    ggplot(., aes(effsize, rating_cl)) +
    geom_jitter() +
    stat_smooth() +
    theme_modern_rc()

study1_w %>% 
    ggplot(., aes(effsize, rating_u3, color = rating_u3_missconcept)) +
    geom_jitter() +
    stat_smooth() +
    theme_modern_rc()

study1_w %>% 
    ggplot(., aes(abs(effsize), rating_ov, color = rating_ov_missconcept)) +
    geom_jitter() +
    stat_smooth(method = "lm") +
    theme_modern_rc()
```

The correlations undermine the interpretation of the misconceptions. Therefore, we will look at the intercorrelations of the dependent variables.

### Compute Kendall's $\tau$ for `accl`, `accu3` and `accov`

```{r}
#| label: kendalls tau
study1_w %>% 
    group_by(type) %>% 
    do(tau_cl = unlist(cor(.$effsize, .$rating_cl, method = "kendall", 
                           use = "pairwise.complete"))) %>% 
    unnest(tau_cl)

study1_w %>% 
    group_by(rating_ov_missconcept, type) %>% 
    do(tau_ov = unlist(cor(abs(.$effsize), .$rating_ov, method = "kendall", 
                           use = "pairwise.complete"))) %>% 
    unnest(tau_ov)

study1_w %>% 
    group_by(rating_u3_missconcept, type) %>% 
    do(tau_u3 = cor(.$effsize, .$rating_u3, method = "kendall", 
                           use = "pairwise.complete")) %>% 
    unnest(tau_u3)
```

### Associations of the Dependent Variables

```{r}
#| label: associactions inter-dv
#| out-height: "30%"
ggplot(study1_w, 
       aes(rating_cl, rating_u3)) +
    geom_jitter() +
    theme_modern_rc() +
ggplot(study1_w, 
       aes(rating_cl, rating_ov)) +
    geom_jitter() +
    theme_modern_rc() +
ggplot(study1_w, 
       aes(rating_ov, rating_u3)) +
    geom_jitter() +
    theme_modern_rc()
```

### Global Under- or Overestimation

```{r}
#| label: under- overestimation
study1_w %>% 
    select(diff_cl, diff_u3_filtered, diff_ov_filtered, session, type) %>% 
    gather(dependent_variable, difference_to_true_effsize, 
           diff_cl, diff_u3_filtered, diff_ov_filtered) %>% 
    ggplot(., aes(type, difference_to_true_effsize)) +
    geom_boxplot(alpha = .3) +
    facet_wrap(~dependent_variable, scales = "free_y") +
    geom_jitter(aes(color = type)) +
    theme_modern_rc() +
    theme(strip.text = element_text(color = "white"),
          axis.text.x = element_blank())
```

# Research Question 1

## Intraclasscorrelations for Accuracy, Perceived Difficulty, Informativity and Value

```{r}
#| label: acc iccs
#| cache: true
icc_mod_rating_cl <- lmer(rating_cl ~  1 + (1|type), 
                          data = study1_w )
icc_mod_rating_u3 <- lmer(rating_u3 ~  1 + (1|type), 
                          data = study1_w %>% 
                              filter(rating_u3_missconcept == F))
icc_mod_rating_ov <- lmer(rating_ov ~  1 + (1|type), 
                          data = study1_w %>% 
                              filter(rating_ov_missconcept == F))
icc_mod_diffi <- lmer(diffi ~  1 + (1|type), 
                      data = study1_w)
icc_mod_infor <- lmer(infor ~  1 + (1|type), 
                      data = study1_w )
icc_mod_value <- lmer(value ~  1 + (1|type), 
                      data = study1_w )

sjPlot::tab_model(
    icc_mod_rating_cl,
    icc_mod_rating_u3,
    icc_mod_rating_ov,
    icc_mod_diffi,
    icc_mod_infor,
    icc_mod_value
)

BF(icc_mod_rating_cl, hypothesis = "icc = 0; icc > 0")
BF(icc_mod_rating_u3, hypothesis = "icc = 0; icc > 0")
BF(icc_mod_rating_ov, hypothesis = "icc = 0; icc > 0")
BF(icc_mod_diffi, hypothesis = "icc = 0; icc > 0")
BF(icc_mod_infor, hypothesis = "icc = 0; icc > 0")
BF(icc_mod_value, hypothesis = "icc = 0; icc > 0")
```

## Random Intercept Models With and Without Visualization Type
```{r}
# Rating Cliffs Delta
mod0_rating_cl <- brm(rating_cl ~ + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
mod1_rating_cl <- brm(rating_cl ~ effsize + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
mod2_rating_cl <- brm(rating_cl ~ type + effsize + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
bayes_factor(mod1_rating_cl, mod0_rating_cl)
bayes_factor(mod2_rating_cl, mod1_rating_cl)

# Rating Cohen's U3
mod0_rating_u3 <- brm(rating_u3 ~ + (1|session), 
                          data = study1_w%>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
mod1_rating_u3 <- brm(rating_u3 ~ effsize + (1|session), 
                          data = study1_w%>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
mod2_rating_u3 <- brm(rating_u3 ~ type + effsize + (1|session), 
                          data = study1_w %>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
bayes_factor(mod1_rating_u3, mod0_rating_u3)
bayes_factor(mod2_rating_u3, mod1_rating_u3)

# Rating Overlap
mod0_rating_ov <- brm(rating_ov ~ + (1|session), 
                          data = study1_w%>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
mod1_rating_ov <- brm(rating_ov ~ effsize + (1|session), 
                          data = study1_w%>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
mod2_rating_ov <- brm(rating_ov ~ type + effsize + (1|session), 
                          data = study1_w %>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
bayes_factor(mod1_rating_ov, mod0_rating_ov)
bayes_factor(mod2_rating_ov, mod1_rating_ov)

# Perceived Difficulty
mod0_diffi <- brm(diffi ~ + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
#mod1_diffi <- brm(diffi ~ effsize + (1|session), 
#                          data = study1_w,
#                          iter = 10000,
#                          save_pars = save_pars(all = TRUE))
mod2_diffi <- brm(diffi ~ type + effsize + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
#bayes_factor(mod1_diffi, mod0_diffi)
#bayes_factor(mod2_diffi, mod1_diffi)
bayes_factor(mod2_diffi, mod0_diffi)

# Perceived Informativity
mod0_infor <- brm(infor ~ + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
#mod1_infor <- brm(infor ~ effsize + (1|session), 
#                          data = study1_w,
#                          iter = 10000,
#                          save_pars = save_pars(all = TRUE))
mod2_infor <- brm(infor ~ type + effsize + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
#bayes_factor(mod1_infor, mod0_infor)
#bayes_factor(mod2_infor, mod1_infor)
bayes_factor(mod2_infor, mod0_infor)

# Perceived Value 
mod0_value <- brm(value ~ + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
#mod1_value <- brm(value ~ effsize + (1|session), 
#                          data = study1_w,
#                          iter = 10000,
#                          save_pars = save_pars(all = TRUE))
mod2_value <- brm(value ~ type + effsize + (1|session), 
                          data = study1_w,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))
#bayes_factor(mod1_value, mod0_value)
#bayes_factor(mod2_value, mod1_value)
bayes_factor(mod2_value, mod0_value)

sjPlot::tab_model(
    mod0_rating_cl, mod0_rating_u3, mod0_rating_ov,
    mod0_diffi, mod0_infor, mod0_value,
    #mod1_rating_cl, mod1_rating_u3, mod1_rating_ov,
    #mod1_diffi, mod1_infor, mod1_value,
    mod2_rating_cl, mod2_rating_u3, mod2_rating_ov,
    mod2_diffi, mod2_infor, mod2_value
    )
```

## Perceived Difficulty

### Graphichal Overview

```{r}
study1_w %>% 
    ggplot(aes(type, diffi)) +
    geom_jitter() +
    stat_summary(fun.data = mean_sdl,
                 fun.args = list(mult = 1),
                 color = "white") +
    theme_modern_rc() +
    labs(title = "Difficulty",
         subtitle = "per Plot Type",
         caption = "Means ± 1*SD")
```


## Perceived Informativity

### Graphical Overview

```{r}
study1_w %>% 
    ggplot(aes(type, infor)) +
    geom_jitter() +
    stat_summary(fun.data = mean_sdl,
                 fun.args = list(mult = 1),
                 color = "white") +
    theme_modern_rc() +
    labs(title = "Informativity",
         subtitle = "per Plot Type",
         caption = "Means ± 1*SD")
```

## Perceived Value

### Graphical Overview

```{r}
study1_w %>% 
    ggplot(aes(type, value)) +
    geom_jitter() +
    stat_summary(fun.data = mean_sdl,
                 fun.args = list(mult = 1),
                 color = "white") +
    theme_modern_rc() +
    labs(title = "Perceived Value",
         subtitle = "per Plot Type",
         caption = "Means ± 1*SD")
```

## Sensitivity

```{r}
#| label: sensi plot

ggplot(study1_w %>% 
           select(sensi_ordinal, type) %>% 
           na.omit(), aes(sensi_ordinal, 
                          color = sensi_ordinal,
                          fill = sensi_ordinal)) +
    facet_wrap(~ type) +
    geom_bar() +
    theme_modern_rc() +
    theme(strip.text = element_text(color = "white")) +
    ggtitle("Sensitivity", "all participants")

ggplot(study1_w %>% 
           select(sensi_ordinal, type, session) %>% 
           na.omit() %>% 
           filter(!session %in% ov_misconceptualizers & 
                      !session %in% u3_misconceptualizers), aes(sensi_ordinal, 
                          color = sensi_ordinal,
                          fill = sensi_ordinal)) +
    facet_wrap(~ type) +
    geom_bar() +
    theme_modern_rc() +
    theme(strip.text = element_text(color = "white")) +
    ggtitle("Sensitivity", "without missconceptualizers")

ggplot(study1_w %>% 
           select(sensi_binary_filtered, type, session),
       aes(sensi_binary_filtered, 
           color = sensi_binary_filtered,
           fill = sensi_binary_filtered)) +
    facet_wrap(~ type) +
    geom_bar() +
    theme_modern_rc() +
    theme(strip.text = element_text(color = "white")) +
    ggtitle("Binary Sensitivity", "without wrong decisions")
```

Fitting a series of logistic regressions with non-informative priors

```{r}
#| label: sensi models
#| cache: true

logreg_mod0 <- brm(sensi_binary_filtered ~ + (1|session), 
                    family = bernoulli(link = "logit"),
                    data = study1_w,
                    save_pars = save_pars(all = TRUE),
                   silent = 2,
                   refresh = 0)
logreg_mod1 <- brm(sensi_binary_filtered ~ effsize_abs + (1|session), 
                   family = bernoulli(link = "logit"),
                   data = study1_w,
                   save_pars = save_pars(all = TRUE),
                   silent = 2,
                   refresh = 0)
logreg_mod2 <- brm(sensi_binary_filtered ~ effsize_abs + type + (1|session), 
                   family = bernoulli(link = "logit"),
                   data = study1_w,
                   save_pars = save_pars(all = TRUE),
                   silent = 2,
                   refresh = 0)
    
bayes_factor(logreg_mod1, logreg_mod0)
bayes_factor(logreg_mod2, logreg_mod1)

sjPlot::tab_model(logreg_mod0, logreg_mod1, logreg_mod2, show.icc = TRUE)

pp_check(logreg_mod2) +
    theme_modern_rc() +
    scale_color_manual(values=viridis(2, begin = .3))
```

## Efficiency
### Visualisation
#### Raw data
```{r}
ggplot(study1_w_timestamp, aes(as.factor(plotNrWithin), effic)) +
    geom_boxplot(alpha = .2, color = "lightgrey") +
    geom_sina(alpha = .5) +
    coord_cartesian(ylim = c(0,100000)) + 
    facet_wrap(~type) +
    theme_modern_rc() +
    labs(title ="Dwell Times Until First Decision",
          subtitle = "Per Plot Type and Plot Repetition") +
    theme(strip.text = element_text(color = "white"))
```

#### 5% Percent Truncated 
```{r}
ggplot(study1_w_timestamp, aes(as.factor(plotNrWithin), effic_05righttrunc)) +
    geom_boxplot(alpha = .2, color = "lightgrey") +
    geom_sina(alpha = .5) +
    coord_cartesian(ylim = c(0,85000)) + 
    facet_wrap(~type) +
    theme_modern_rc() +
    labs(title ="5% Truncated Dwell Times Until First Decision",
          subtitle = "Per Plot Type and Plot Repetition") +
    theme(strip.text = element_text(color = "white"))
```

#### 10% Percent Truncated 
```{r}
ggplot(study1_w_timestamp, aes(as.factor(plotNrWithin), effic_10righttrunc)) +
    geom_boxplot(alpha = .2, color = "lightgrey") +
    geom_sina(alpha = .5) +
    coord_cartesian(ylim = c(0,85000)) + 
    facet_wrap(~type) +
    theme_modern_rc() +
    labs(title ="10% Truncated Dwell Times Until First Decision",
          subtitle = "Per Plot Type and Plot Repetition") +
    theme(strip.text = element_text(color = "white"))
```

#### `log()` Transformed 
```{r}
ggplot(study1_w_timestamp, 
       aes(as.factor(plotNrWithin), 
           log(effic_05righttrunc))) +
    geom_boxplot(alpha = .2, color = "lightgrey") +
    geom_sina(alpha = .5) +
    facet_wrap(~type) +
    theme_modern_rc() +
    labs(title ="log Transformed Dwell Times Until First Decision",
          subtitle = "Per Plot Type and Plot Repetition") +
    theme(strip.text = element_text(color = "white"))
```

### Modeling with `{brms}`
#### Efficiency for First Plot
We fitted models and assumed truncated (lower bound lb = 0) t-distributions for the response variable ..
```{r}
#| cache: true
#| error: false
#| warning: false
#| results: hide

plot01_mod0 <- 
    brm(effic | trunc(lb = 0) ~ 1 + (1|session),
    data = study1_w_timestamp %>% 
        filter(plotNrWithin == 1),
    family = "student", # Due to the self-paced participation in online surveys, implausible values (e.g. extreme outliers due to time away from keyboard) may have occurred and led to heavily skewed distributions. 
    save_pars = save_pars(all = TRUE),
    #silent = 2,
    #refresh = 0,
    iter = 2000)

pp_check(plot01_mod0) +
    xlim(c(0,250000)) +
    theme_modern_rc() +
    scale_color_manual(values=viridis(2, begin = .3))

plot01_mod1 <- 
    brm(effic | trunc(lb = 0) ~ 1 + type + (1|session),
    data = study1_w_timestamp %>% 
        filter(plotNrWithin == 1),
    family = "student",
    save_pars = save_pars(all = TRUE)#,
   # silent = 2,
   # refresh = 0,
   # iter = 15000
    )

pp_check(plot01_mod1) +
    xlim(c(0,250000)) +
    theme_modern_rc() +
    scale_color_manual(values=viridis(2, begin = .3))
```


```{r}
sjPlot::tab_model(plot01_mod0, plot01_mod1)
bayes_factor(plot01_mod1, plot01_mod0,
             repetitions = 3)
```

#### Efficiency for Last Three Plots
```{r}
#| cache: true
#| error: false
#| warning: false
#| results: hide
plot0306_mod0 <- 
    brm(effic | trunc(lb = 0) ~ 1 + plotNrWithin_factor + (1|session),
    data = study1_w_timestamp %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000)

pp_check(plot0306_mod0) +
    xlim(c(0,250000)) +
    theme_modern_rc() +
    scale_color_manual(values=viridis(2, begin = .3))

plot0306_mod1 <- 
    brm(effic | trunc(lb = 0) ~ 1 + plotNrWithin_factor + type + (1|session),
    data = study1_w_timestamp %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 35000,
    cores = 8)

pp_check(plot0306_mod1) +
    xlim(c(0,250000)) +
    theme_modern_rc() +
    scale_color_manual(values=viridis(2, begin = .3))
```


```{r}
sjPlot::tab_model(plot0306_mod0, plot0306_mod1)
bayes_factor(plot0306_mod1, plot0306_mod0,
             rep = 3) # add repetitions as warning messages informed about estimates that might be more variable than usual. Repetitions indicate that the estimates actually vary. However, the results fluctuate in a range where extreme evidence for H1 can always be assumed.
```


# Research Question 2

## Contrast Effects 

 ### Graphical Overview
```{r}
# preparing mulilevel model with brms for graphical overview
library(ggdist)
library(patchwork)
library(tidybayes)

# rating u3
mod_plot_ratingu3 <- brm (scale(rating_u3) ~ (1|type),
                 data = study1_w,
                   prior = c(
    prior(normal(0, 1), class = Intercept),
    prior(student_t(3, 0, 1), class = sd),
    prior(student_t(3, 0, 1), class = sigma)
  ),
  control = list(adapt_delta = .99)
  ) 

plot_ratingu3 <- mod_plot_ratingu3 %>%
  spread_draws(b_Intercept, r_type[type,]) %>%
 # median_qi(type_mean = b_Intercept + r_type, .width = c(.95, .66)) %>%
  mutate(type_mean = b_Intercept + r_type) %>%
  ggplot(aes(y = type, x = type_mean
             #xmin = .lower, xmax = .upper
             )) +
#  geom_pointinterval() +
    stat_halfeye() +
    theme_ipsum_rc() +
    theme(axis.title.x = element_blank(),
          axis.text.y = element_text(hjust = 0)) +
    #scale_x_continuous(limits=c(-0.6, 0.6)) +
    ggtitle('Accuracy in U3 Metrics')
plot_ratingu3

# rating ov
mod_plot_ratingov <- brm (scale(rating_ov) ~ (1|type),
                 data = study1_w,
                   prior = c(
    prior(normal(0, 1), class = Intercept),
    prior(student_t(3, 0, 1), class = sd),
    prior(student_t(3, 0, 1), class = sigma)
  ),
  control = list(adapt_delta = .99)
  )

plot_ratingov <-mod_plot_ratingov %>%
  spread_draws(b_Intercept, r_type[type,]) %>%
 # median_qi(type_mean = b_Intercept + r_type, .width = c(.95, .66)) %>%
  mutate(type_mean = b_Intercept + r_type) %>%
  ggplot(aes(y = type, x = type_mean
             #xmin = .lower, xmax = .upper
             )) +
#  geom_pointinterval() +
    stat_halfeye() + 
    theme_ipsum_rc()+
    theme(axis.title.x = element_blank(),
          axis.text.y = element_blank(), 
          axis.title.y = element_blank()) +
    #scale_x_continuous(limits=c(-0.6, 0.6)) +
    ggtitle('Accuracy in Overlap Metrics')
plot_ratingov

# difficulty
mod_plot_diffi <- brm (scale(diffi) ~ (1|type),
                 data = study1_w,
                   prior = c(
    prior(normal(0, 1), class = Intercept),
    prior(student_t(3, 0, 1), class = sd),
    prior(student_t(3, 0, 1), class = sigma)
  ),
  control = list(adapt_delta = .99)
  )

plot_diffi <- mod_plot_diffi %>%
  spread_draws(b_Intercept, r_type[type,]) %>%
 # median_qi(type_mean = b_Intercept + r_type, .width = c(.95, .66)) %>%
  mutate(type_mean = b_Intercept + r_type) %>%
  ggplot(aes(y = type, x = type_mean
             #xmin = .lower, xmax = .upper
             )) +
#  geom_pointinterval() +
    stat_halfeye() +
    theme_ipsum_rc() +
    theme(axis.title.x = element_blank(),
          axis.text.y = element_blank(), 
          axis.title.y = element_blank()) +
    #scale_x_continuous(limits=c(-0.6, 0.6)) +
    ggtitle('Perceived Task Difficulty')
plot_diffi


# informativity
mod_plot_infor <- brm (scale(infor) ~ (1|type),
                 data = study1_w,
                   prior = c(
    prior(normal(0, 1), class = Intercept),
    prior(student_t(3, 0, 1), class = sd),
    prior(student_t(3, 0, 1), class = sigma)
  ),
  control = list(adapt_delta = .99)
  )

plot_infor <- mod_plot_infor %>%
  spread_draws(b_Intercept, r_type[type,]) %>%
 # median_qi(type_mean = b_Intercept + r_type, .width = c(.95, .66)) %>%
  mutate(type_mean = b_Intercept + r_type) %>%
  ggplot(aes(y = type, x = type_mean #xmin = .lower, xmax = .upper
             )) +
#  geom_pointinterval() +
  stat_halfeye() +
    theme_ipsum_rc() +
    theme(axis.title.x = element_blank(),
          axis.text.y = element_text(hjust = 0)) +
    #scale_x_continuous(limits=c(-0.6, 0.6)) +
    ggtitle('Perceived Informativity')

plot_infor

# value 

mod_plot_value <- brm (scale(value) ~ (1|type),
                 data = study1_w,
                   prior = c(
    prior(normal(0, 1), class = Intercept),
    prior(student_t(3, 0, 1), class = sd),
    prior(student_t(3, 0, 1), class = sigma)
  ),
  control = list(adapt_delta = .99)
  )

plot_value <- mod_plot_value %>%
  spread_draws(b_Intercept, r_type[type,]) %>%
 # median_qi(type_mean = b_Intercept + r_type, .width = c(.95, .66)) %>%
  mutate(type_mean = b_Intercept + r_type) %>%
  ggplot(aes(y = type, x = type_mean #xmin = .lower, xmax = .upper
             )) +
#  geom_pointinterval() +
  stat_halfeye() +
    theme_ipsum_rc() +
    theme(axis.title.x = element_blank(),
          axis.text.y = element_blank(), 
          axis.title.y = element_blank()) +
    #scale_x_continuous(limits=c(-0.6, 0.6)) +
    ggtitle('Perceived Value')

plot_value

#study1_w %>% 
#    select(rating_cl, rating_u3_filtered, rating_ov_filtered,
#           diffi, infor, value, type) %>% 
#    pivot_longer(names_to = "Dependent Variable",
#                 values_to = "Rating", 
#                 cols =  c(rating_cl, rating_u3_filtered, #rating_ov_filtered,
#                           diffi, infor)) %>% 
#    ggplot(aes(Rating, type)) +
#    geom_dots() +
#    stat_slab(aes(fill = stat(level)), .width = c(.66, .95, 1),
#              alpha = .3) +
#    facet_wrap(~`Dependent Variable`, 
#               ncol = 6,
#               scales = "free") +
#    theme_ipsum_rc()
#    
```


### Model Contrast Effects with `{brms}`

```{r}
# create dummy variables to compare visualization types for those measures that showed evidence for difference (accuracy U3, accuracy overlap, perceived task difficulty, perceived informativity, perceived value, efficiency)

## Gardner Altman Plot vs. Halfeye xaxis
gardneraltman_vs_halfeye_x <- study1_w %>%
    group_by(session) %>%
    mutate(dummy_gardneraltman_halfeye_x = 
               case_when(type == "gardneraltman_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "gardneraltman_xaxis" | type == "halfeye_xaxis") %>%
    ungroup()

gardneraltman_vs_halfeye_x_effic <- study1_w_timestamp %>%
    group_by(session) %>%
    mutate(dummy_gardneraltman_halfeye_x = 
               case_when(type == "gardneraltman_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "gardneraltman_xaxis" | type == "halfeye_xaxis") %>%
    ungroup() # %>% 
   # full_join(study1_w %>% select(session, effsize), by = "session")

mod_accu3_gardneraltman_halfeye_x <- 
    brm(scale(rating_u3) ~ dummy_gardneraltman_halfeye_x + effsize + (1|session), 
                          data = gardneraltman_vs_halfeye_x%>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_accov_gardneraltman_halfeye_x <- 
    brm(scale(rating_ov) ~ dummy_gardneraltman_halfeye_x + effsize + (1|session), 
                          data = gardneraltman_vs_halfeye_x%>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_diffi_gardneraltman_halfeye_x <- 
    brm(scale(diffi) ~ dummy_gardneraltman_halfeye_x #+ effsize 
        + (1|session), 
                          data = gardneraltman_vs_halfeye_x,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_infor_gardneraltman_halfeye_x <- 
    brm(scale(infor) ~ dummy_gardneraltman_halfeye_x #+ effsize
        + (1|session), 
                          data = gardneraltman_vs_halfeye_x,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_value_gardneraltman_halfeye_x <- 
    brm(scale(value) ~ dummy_gardneraltman_halfeye_x #+ effsize 
        + (1|session), 
                          data = gardneraltman_vs_halfeye_x,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))


mod_effic01_gardneraltman_halfeye_x <- 
    brm(effic | trunc(lb = 0) ~ dummy_gardneraltman_halfeye_x + (1|session),
    data = gardneraltman_vs_halfeye_x_effic %>%  
    filter(plotNrWithin == 1),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000
    )

mod_effic0306_gardneraltman_halfeye_x <- 
    brm(effic | trunc(lb = 0) ~ dummy_gardneraltman_halfeye_x +
            (1|session),
    data = gardneraltman_vs_halfeye_x_effic %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000,
    cores = 8)

                  
## Gardner Altman Plot vs. Halfeye yaxis
gardneraltman_vs_halfeye_y <- study1_w %>%
    group_by(session) %>%
    mutate(dummy_gardneraltman_halfeye_y = 
               case_when(type == "gardneraltman_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "gardneraltman_xaxis" | type == "halfeye_yaxis") %>%
    ungroup()

gardneraltman_vs_halfeye_y_effic <- study1_w_timestamp %>%
    group_by(session) %>%
    mutate(dummy_gardneraltman_halfeye_y = 
               case_when(type == "gardneraltman_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "gardneraltman_xaxis" | type == "halfeye_yaxis") %>%
    ungroup() # %>% 
   # full_join(study1_w %>% select(session, effsize), by = "session")


mod_accu3_gardneraltman_halfeye_y <- 
    brm(scale(rating_u3) ~ dummy_gardneraltman_halfeye_y + effsize + (1|session), 
                          data = gardneraltman_vs_halfeye_y%>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_accov_gardneraltman_halfeye_y <- 
    brm(scale(rating_ov) ~ dummy_gardneraltman_halfeye_y + effsize + (1|session), 
                          data = gardneraltman_vs_halfeye_y%>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_diffi_gardneraltman_halfeye_y <- 
    brm(scale(diffi) ~ dummy_gardneraltman_halfeye_y #+ effsize 
        + (1|session), 
                          data = gardneraltman_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_infor_gardneraltman_halfeye_y <- 
    brm(scale(infor) ~ dummy_gardneraltman_halfeye_y #+ effsize 
        + (1|session), 
                          data = gardneraltman_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_value_gardneraltman_halfeye_y <- 
    brm(scale(value) ~ dummy_gardneraltman_halfeye_y #+ effsize 
        + (1|session), 
                          data = gardneraltman_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_effic01_gardneraltman_halfeye_y <- 
    brm(effic | trunc(lb = 0) ~ dummy_gardneraltman_halfeye_y + (1|session),
    data = gardneraltman_vs_halfeye_y_effic %>%  
    filter(plotNrWithin == 1),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000
    )

mod_effic0306_gardneraltman_halfeye_y <- 
    brm(effic | trunc(lb = 0) ~ dummy_gardneraltman_halfeye_y +
            (1|session),
    data = gardneraltman_vs_halfeye_y_effic %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000,
    cores = 8)

## Raincloud Plot vs. Halfeye x axis
raincloud_vs_halfeye_x <- study1_w %>%
    group_by(session) %>%
    mutate(dummy_raincloud_halfeye_x = 
               case_when(type == "raincloud_yaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "halfeye_xaxis" | type == "raincloud_yaxis") %>%
    ungroup()

raincloud_vs_halfeye_x_effic <- study1_w_timestamp %>%
    group_by(session) %>%
    mutate(dummy_raincloud_halfeye_x = 
               case_when(type == "raincloud_yaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "raincloud_yaxis" | type == "halfeye_xaxis") %>%
    ungroup() # %>% 
   # full_join(study1_w %>% select(session, effsize), by = "session")

mod_accu3_raincloud_halfeye_x <- 
    brm(scale(rating_u3) ~ dummy_raincloud_halfeye_x + effsize + (1|session), 
                          data = raincloud_vs_halfeye_x %>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_accov_raincloud_halfeye_x <- 
    brm(scale(rating_ov) ~ dummy_raincloud_halfeye_x + effsize + (1|session), 
                          data = raincloud_vs_halfeye_x %>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_diffi_raincloud_halfeye_x <- 
    brm(scale(diffi) ~ dummy_raincloud_halfeye_x #+ effsize 
        + (1|session), 
                          data = raincloud_vs_halfeye_x,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_infor_raincloud_halfeye_x <- 
    brm(scale(infor) ~ dummy_raincloud_halfeye_x #+ effsize 
        + (1|session), 
                          data = raincloud_vs_halfeye_x,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_value_raincloud_halfeye_x <- 
    brm(scale(value) ~ dummy_raincloud_halfeye_x #+ effsize 
        + (1|session), 
                          data = raincloud_vs_halfeye_x,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_effic01_raincloud_halfeye_x <- 
    brm(effic | trunc(lb = 0) ~ dummy_raincloud_halfeye_x + (1|session),
    data = raincloud_vs_halfeye_x_effic %>%  
    filter(plotNrWithin == 1),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000
    )

mod_effic0306_raincloud_halfeye_x <- 
    brm(effic | trunc(lb = 0) ~ dummy_raincloud_halfeye_x +
            (1|session),
    data = raincloud_vs_halfeye_x_effic %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000,
    cores = 8)

##  Raincloud Plot vs.Halfeye yaxis
raincloud_vs_halfeye_y <- study1_w %>%
    group_by(session) %>%
    mutate(dummy_raincloud_halfeye_y = 
               case_when(type == "raincloud_yaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "halfeye_yaxis" | type == "raincloud_yaxis") %>%
    ungroup()

raincloud_vs_halfeye_y_effic <- study1_w_timestamp %>%
    group_by(session) %>%
    mutate(dummy_gardneraltman_halfeye_x = 
               case_when(type == "raincloud_yaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "raincloud_yaxis" | type == "halfeye_yaxis") %>%
    ungroup() # %>% 
   # full_join(study1_w %>% select(session, effsize), by = "session")

mod_accu3_raincloud_halfeye_y <- 
    brm(scale(rating_u3) ~ dummy_raincloud_halfeye_y + effsize + (1|session), 
                          data = raincloud_vs_halfeye_y %>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_accov_raincloud_halfeye_y <- 
    brm(scale(rating_ov) ~ dummy_raincloud_halfeye_y + effsize + (1|session), 
                          data = raincloud_vs_halfeye_y %>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_diffi_raincloud_halfeye_y <- 
    brm(scale(diffi) ~ dummy_raincloud_halfeye_y #+ effsize 
        + (1|session), 
                          data = raincloud_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_infor_raincloud_halfeye_y <- 
    brm(scale(infor) ~ dummy_raincloud_halfeye_y #+ effsize 
        + (1|session), 
                          data = raincloud_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_value_raincloud_halfeye_y <- 
    brm(scale(value) ~ dummy_raincloud_halfeye_y #+ effsize 
        + (1|session), 
                          data = raincloud_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_effic01_raincloud_halfeye_y <- 
    brm(effic | trunc(lb = 0) ~ dummy_raincloud_halfeye_y + (1|session),
    data = raincloud_vs_halfeye_y_effic %>%  
    filter(plotNrWithin == 1),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000
    )

mod_effic0306_raincloud_halfeye_y <- 
    brm(effic | trunc(lb = 0) ~ dummy_raincloud_halfeye_y +
            (1|session),
    data = raincloud_vs_halfeye_y_effic %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000,
    cores = 8)

sjPlot::tab_model(mod_accu3_gardneraltman_halfeye_x, 
        mod_accov_gardneraltman_halfeye_x, mod_diffi_gardneraltman_halfeye_x, 
        mod_infor_gardneraltman_halfeye_x, mod_value_gardneraltman_halfeye_x,
        mod_effic01_gardneraltman_halfeye_x, mod_effic0306_gardneraltman_halfeye_x,
        mod_accu3_gardneraltman_halfeye_y, mod_accov_gardneraltman_halfeye_y, 
        mod_diffi_gardneraltman_halfeye_y, mod_infor_gardneraltman_halfeye_y, 
        mod_value_gardneraltman_halfeye_y,
        mod_effic01_gardneraltman_halfeye_y, mod_effic0306_gardneraltman_halfeye_y,
        mod_accov_raincloud_halfeye_x, mod_diffi_raincloud_halfeye_x, 
        mod_infor_raincloud_halfeye_x, mod_value_raincloud_halfeye_x,
        mod_effic01_raincloud_halfeye_x, mod_effic0306_raincloud_halfeye_x,
        mod_accu3_raincloud_halfeye_y, mod_accov_raincloud_halfeye_y, 
        mod_diffi_raincloud_halfeye_y, mod_infor_raincloud_halfeye_y, 
        mod_value_raincloud_halfeye_y,
        mod_effic01_raincloud_halfeye_y, mod_effic0306_raincloud_halfeye_y)
    
## Gardner Altman Plot vs. Raincloud Plot
gardneraltman_vs_raincloud <- study1_w %>%
    group_by(session) %>%
    mutate(dummy_gardneraltman_raincloud = 
               case_when(type == "gardneraltman_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "gardneraltman_xaxis" | type == "raincloud_yaxis") %>%
    ungroup()

gardneraltman_vs_raincloud_effic <- study1_w_timestamp %>%
    group_by(session) %>%
    mutate(dummy_gardneraltman_halfeye_x = 
               case_when(type == "gardneraltman_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "gardneraltman_xaxis" | type == "raincloud_yaxis") %>%
    ungroup() # %>% 
   # full_join(study1_w %>% select(session, effsize), by = "session")

mod_accu3_gardneraltman_raincloud <- 
    brm(scale(rating_u3) ~ dummy_gardneraltman_raincloud + effsize + (1|session), 
                          data = gardneraltman_vs_raincloud%>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_accov_gardneraltman_raincloud <- 
    brm(scale(rating_ov) ~ dummy_gardneraltman_raincloud + effsize + (1|session), 
                          data = gardneraltman_vs_raincloud%>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_diffi_gardneraltman_raincloud <- 
    brm(scale(diffi) ~ dummy_gardneraltman_raincloud #+ effsize
        + (1|session), 
                          data = gardneraltman_vs_raincloud,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_infor_gardneraltman_raincloud <- 
    brm(scale(infor) ~ dummy_gardneraltman_raincloud #+ effsize
        + (1|session), 
                          data = gardneraltman_vs_raincloud,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_value_gardneraltman_raincloud <- 
    brm(scale(value) ~ dummy_gardneraltman_raincloud #+ effsize
        + (1|session), 
                          data = gardneraltman_vs_raincloud,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_effic01_gardneraltman_raincloud <- 
    brm(effic | trunc(lb = 0) ~ dummy_gardneraltman_raincloud + (1|session),
    data = gardneraltman_vs_raincloud_effic %>%  
    filter(plotNrWithin == 1),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000
    )

mod_effic0306_gardneraltman_raincloud <- 
    brm(effic | trunc(lb = 0) ~ dummy_gardneraltman_raincloud +
            (1|session),
    data = gardneraltman_vs_raincloud_effic %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000,
    cores = 8)

## Halfeye xaxis vs. Halfeye yaxis

halfeye_x_vs_halfeye_y <- study1_w %>%
    group_by(session) %>%
    mutate(dummy_halfeye_x_halfeye_y = 
               case_when(type == "halfeye_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "halfeye_xaxis" | type == "halfeye_yaxis") %>%
    ungroup()

halfeye_x_vs_halfeye_y <- study1_w %>%
    group_by(session) %>%
    mutate(dummy_raincloud_halfeye_y = 
               case_when(type == "halfeye_xaxis" ~ 0, TRUE ~ 1)) %>%
    filter(type == "halfeye_xaxis" | type == "halfeye_yaxis") %>%
    ungroup()

mod_accu3_halfeye_x_halfeye_y <- 
    brm(scale(rating_u3) ~ dummy_halfeye_x_halfeye_y + effsize + (1|session), 
                          data = halfeye_x_vs_halfeye_y %>% 
                              filter(rating_u3_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_accov_halfeye_x_halfeye_y <- 
    brm(scale(rating_ov) ~ dummy_halfeye_x_halfeye_y + effsize + (1|session), 
                          data = halfeye_x_vs_halfeye_y%>% 
                              filter(rating_ov_missconcept == F),
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_diffi_halfeye_x_halfeye_y <- 
    brm(scale(diffi) ~ dummy_halfeye_x_halfeye_y #+ effsize 
        + (1|session), 
                          data = halfeye_x_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_infor_halfeye_x_halfeye_y <- 
    brm(scale(infor) ~ dummy_halfeye_x_halfeye_y #+ effsize 
        + (1|session), 
                          data = halfeye_x_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_value_halfeye_x_halfeye_y <- 
    brm(scale(value) ~ dummy_halfeye_x_halfeye_y #+ effsize 
        + (1|session), 
                          data = halfeye_x_vs_halfeye_y,
                          iter = 10000,
                          save_pars = save_pars(all = TRUE))

mod_effic01_halfeye_x_halfeye_y <- 
    brm(effic | trunc(lb = 0) ~ dummy_halfeye_x_halfeye_y + (1|session),
    data = halfeye_x_vs_halfeye_y %>%  
    filter(plotNrWithin == 1),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000
    )

mod_effic0306_halfeye_x_halfeye_y <- 
    brm(effic | trunc(lb = 0) ~ dummy_halfeye_x_halfeye_y +
            (1|session),
    data = halfeye_x_vs_halfeye_y %>% 
        filter(plotNrWithin >= 4),
    family = "student",
    save_pars = save_pars(all = TRUE),
    silent = 2,
    refresh = 0,
    iter = 15000,
    cores = 8)

sjPlot::tab_model(mod_accu3_halfeye_x_halfeye_y, mod_accov_halfeye_x_halfeye_y, 
                  mod_diffi_halfeye_x_halfeye_y, mod_infor_halfeye_x_halfeye_y, 
                  mod_value_halfeye_x_halfeye_y,
                  mod_effic01_halfeye_x_halfeye_y, 
                  mod_effic0306_halfeye_x_halfeye_y,
                  mod_accu3_gardneraltman_raincloud, 
                  mod_accov_gardneraltman_raincloud, 
                  mod_diffi_gardneraltman_raincloud, 
                  mod_infor_gardneraltman_raincloud, 
                  mod_value_gardneraltman_raincloud,
                  mod_effic01_gardneraltman_raincloud, 
                  mod_effic0306_gardneraltman_raincloud)
```


